### 2015-07-21 doc/manual/overview.tex

This manual describes ``version 3'' of \sfincs.  
To preserve previous versions of the code that have been used for publications, two older versions of the
code called singleSpecies and multiSpecies are also present in the repository.  For both of these older versions,
both MATLAB and fortran editions exist which are independent of each other.  At present, version 3 exists
only in a fortran edition.

>>>>

This manual describes ``version 3'' of \sfincs.  
To preserve previous versions of the code that have been used for publications, two older versions of the
code called singleSpecies and multiSpecies are also present in the repository.  
For all versions, both MATLAB and fortran editions exist which are independent of each other.
The MATLAB editions exist primarily for debugging the fortran editions.
The same algorithms are implemented in the two different languages, and for identical input parameters, 
the matrices and output quantities from the different editions should agree to several significant digits (roughly within the solver tolerance.)
Any significant differences between the matrices and output of the MATLAB and fortran editions can be used to identify a bug.
The MATLAB versions are serial whereas the fortran versions
are parallelized, so the fortran versions are significantly faster and can access much more memory.
For realistic experimental geometry and collisionality, the resolution (and hence memory) requirements will mean
you will need to use the fortran edition.
